Continuous developmental changes in word recognition support language learning across early childhood

### 2025-04-04 0_get_data.qmd
recached intermediates

save(aoi_data_joined, file= here("cached_intermediates","0_aoi_data_joined.Rds"))
```

@@

```{r}
load(here("cached_intermediates", "1_aoi_data_joined.Rds"))
length(unique(aoi_data_joined$dataset_name))
unique(aoi_data_joined$dataset_name)
```

@@

save(d_aoi, file = here("cached_intermediates","1_d_aoi.Rds"))
```

@@

save(cdi_data, file=here("cached_intermediates", "0_cdi_subjects.Rds"))
```

>>>>

saveRDS(aoi_data_joined, file= here("cached_intermediates","0_aoi_data_joined.Rds"))
```

@@

```{r}
aoi_data_joined <- readRDS(here("cached_intermediates", "1_aoi_data_joined.Rds"))
length(unique(aoi_data_joined$dataset_name))
unique(aoi_data_joined$dataset_name)
```

@@

saveRDS(d_aoi, file = here("cached_intermediates","0_d_aoi.Rds"))
```

@@

saveRDS(cdi_data, file=here("cached_intermediates", "0_cdi_subjects.Rds"))
```

### 2025-04-04 paper/paper.Rmd
recached intermediates

#load d_aoi for timecourse plot
d_aoi <- readRDS(here("cached_intermediates","1_d_aoi.Rds"))
d_trial <- readRDS(here("cached_intermediates","1_d_trial.Rds")) |>
  mutate(log_age = log(age))
d_sub <- readRDS(here("cached_intermediates","1_d_sub.Rds")) |>
  group_by(subject_id) |>
  arrange(age) |>
  mutate(admin_num = 1:n(), 
         time_since_t0 = age - age[1],
         delta_t = c(0, diff(age)))

>>>>

#load d_aoi for timecourse plot
d_aoi <- readRDS(here("cached_intermediates","0_d_aoi.Rds"))
d_trial <- readRDS(here("cached_intermediates","1_d_trial.Rds")) |>
  mutate(log_age = log(age))
d_sub <- readRDS(here("cached_intermediates","1_d_sub.Rds")) |>
  group_by(subject_id) |>
  arrange(age) |>
  mutate(admin_num = 1:n(), 
         time_since_t0 = age - age[1],
         delta_t = c(0, diff(age)))
